---
output:
  github_document:
    html_preview: true
params:
  diag: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# study.sankey

Available at:

- Site: <https://fcacollin.github.io/study.sankey>
- Source: <https://github.com/FCACollin/study.sankey>

```bash
git clone https://github.com/FCACollin/study.sankey.git
```

```{r setup}
knitr::opts_chunk$set(
  comment = "#>",
  echo = TRUE,
  error = TRUE,
  fig.path = "man/figures/README-",
  comment = "#>",
  out.width = "100%",
  fig.height = 8.3 * .66,
  fig.width = 11.7 * .66,
  dpi = 300
)
```
# 1. Controlled execution

As any R Markdown file, the `params` argument in the YAML front matter offers
controlled-execution settings. For instance:

- when the following parameter is used:

```yaml
params:
  diag: true
```
  
- this code chunk is evaluated and included:

````
```{r, check, eval=params$diag, include=params$diag}`r ''`
devtools::check(quiet = TRUE)
```
````

- note: `devtools::check()` provides diagnostic/quality information
  about the package but is lengthy, hence the rendering time is substantially
  increased for `diag: true`.

```{r, check, eval=params$diag, include=params$diag}
devtools::check(quiet = TRUE)
```

The code chunks in `inst/study.R` are identified by `knitr::read_chunk()`;
then can then selectively called from the `README.Rmd` file.

```{r readchunks}
file_nm <- "inst/study.R"
knitr::read_chunk(file_nm)
message("R code chunks read from:\n", file_nm)
```

## 2. Analysis

```{r, settings}
```

### 2.1. Dataset preparation

```{r, data_adam}
```

```{r, analysis_dataset}
```

### 2.2. Graphics

```{r, graphic}
```

```{r, annotation}
```
